\chapter*{Acknowledgements}

Firstly, I submit my reverential pranams at the lotus feet of His Holiness Parama Poojya Jagadguru Shree Shree Shree Shivarathri Deshikendra Mahaswamigalavaru, President, JSS Mahavidya Peetha, Mysore. His divine blessings has always been a continuous source of inspiration to all my endeavours.

\thispagestyle{empty}

\vskip .1cm
I greatfully acknowledge all the encouragement and support rendered by Dr. Syed Shakheeb Ur Rehman, Principal, SJCE, Mysore in drafting this book.

\vskip .1cm
I deeply remember Late Dr. R. D. Sudhakar Samuel, my teacher, my former H.O.D., who taught me the art of book writing.

\vskip .1cm
I must acknowledge the support and encouragement rendered by Dr. M. N. Shanmukha Swamy, Head of EC department, SJCE, Mysore.

\vskip .1cm
My heart felt thanks to my friend, colleague Prof. V. Nattarasu for his continuous support and guidance in making this book.

\vskip .1cm
I must acknowledge the support and encouraging words rendered by my teacher, colleague and my well wisher Prof. Dr. Chamaraju of Mathematics Department, SJCE, Mysore, in making this book.

\vskip .1cm
I also thank my colleague Dr. Shankaraih, Professor, ED Department, SJCE, Mysore for his support in making this book.

\vskip .1cm
I thank Mr. R. Subramanian of Sanguine Technical Publishers for his meticulous review of this book and valuable suggestions for improving the quality of this book.

\vskip .1cm
My special thanks to Smt. Rashmi S., Assistant Professor, EEE Department, VVCE, Mysore for her sincere effort in reviewing the content of this book several times and her valuable suggestions for improving the quality of this book both in technical as well as conceptual presentation aspects. Her husband G. V. Krishna also needs a special mention for his encouraging works while drafting this book.

\vskip .1cm
I must acknowledge all the encouragement and support from my wife Smt. K. S. Umadevi and my son Jeevan M. Swamy in making this project a success. The encouraging words of my brother Mr. B. Chandra Shekara Murthy, Quality Control Engineer, Muscat, over phone is unforgettable.


\thispagestyle{empty}

\vskip .1cm
I cheers in my heart, the heartfelt blessings of my mother Smt. K. P. Leelavathy at each and every stage of drafting this book. The support rendered by all my family members need a special mention.

\vskip .1cm
Finally I express my sincere gratitude to Sanguine Publishers for their constant support to convert my dreams into reality.

\bigskip
\bigskip
\hfill {\bf Dr. U. B. Mahadevaswamy\qquad}   
